---
title: "The workplanr Packge"
author: "David Hammond"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

> "Plans are worthless, but planning is everything."
([Dwight D. Eisenhower](https://quoteinvestigator.com/2017/11/18/planning/))

```{r setup, include = FALSE, messages = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Required inputs to workplanr

```{r library, include = TRUE, results='hide', message=FALSE, warning=FALSE}
library(workplanr)
```

### Resources

```{r resources, include = TRUE, results='hide', message=FALSE, warning=FALSE}
staff <- c("Shelby", "Luis", "Taishawn", "Samantha", "Taylor", "unassigned")
staff_capacity <- c(40,60,100,100,100, 100)
```

The `html_vignette` template includes a basic CSS theme. To override this theme you can specify your own CSS in the document metadata as follows:

    output: 
      rmarkdown::html_vignette:
        css: mystyles.css

### Projects

```{r projects, include = TRUE, results='hide', message=FALSE, warning=FALSE}
projects <- LETTERS[1:3]
project_probability <- c(50, 100, 100)
project_start <- as.Date(c("2019-01-25", "2019-05-17", "2019-06-27"))
project_end <- as.Date(c("2019-06-03", "2019-06-16", "2019-09-27"))
project_phases <- c("research", "drafting", "editing", "design", "print", "events")
project_time_estimates  <- c(c(-10,-10,-10,-10,-10,-10), c(-10,-10,-10,-10,-10,-10), c(-10,-10,-10,10,10,10)) 
```
### Staff Leave

```{r leave, include = TRUE, results='hide', message=FALSE, warning=FALSE}
staff_on_leave <- c("Luis", "Samantha")
leave_start <-  as.Date(c("2019-07-23", "2019-05-16"))
leave_end <- leave_start + c(20, 25)
leave_description <- c("leave", "work trip")
```


### Public/Bank Holidays

```{r holidays, include = TRUE, results='hide', message=FALSE, warning=FALSE}
url <- "https://data.gov.au/data/dataset/b1bc6077-dadd-4f61-9f8c-002ab2cdff10/resource/31eec35e-1de6-4f04-9703-9be1d43d405b/download/australian_public_holidays_2019.csv"
public_holidays <- utils::read.csv(url, stringsAsFactors = FALSE)
names(public_holidays) <- tolower(names(public_holidays))
public_holidays$date <- as.Date(lubridate::ymd(public_holidays$date))
public_holidays <- public_holidays %>% filter(jurisdiction == "nsw") %>%
  select(date, holiday.name) %>% rename(name = holiday.name)
public_holidays_date <- public_holidays$date
public_holidays_name = public_holidays$name
```


### Assigning staff time to projects

```{r assignments, include = TRUE, results='hide', message=FALSE, warning=FALSE}
#staff project assignments
staff_project_assignment_capacity <- sample(c(0,25,50,75,100), size = length(projects)*length(project_phases)*length(staff), replace = T)
```

### Getting your workplan

```{r get_workplan, include = TRUE, results='hide', message=FALSE, warning=FALSE}
wp <- get_workplan(staff = staff, 
                    staff_capacity = staff_capacity,
                    projects = projects, 
                    project_probability =  project_probability, 
                    project_start = project_start, 
                    project_end = project_end, 
                    project_phases = project_phases, 
                    project_time_estimates = project_time_estimates, 
                    staff_on_leave = staff_on_leave, 
                    leave_start = leave_start, 
                    leave_end = leave_end, 
                    leave_description = leave_description, 
                    public_holidays_date = public_holidays_date,
                    public_holidays_name = public_holidays_name,
                    staff_project_assignment_capacity = staff_project_assignment_capacity)
```

### Plot Staff Schedule and Workload
```{r plot_staff_schedule, fig.height = 6, fig.width = 8, include = TRUE, results='hide', message=FALSE, warning=FALSE}
plot(wp@staff_schedule)
```

### Plot Team Workload
```{r plot_team_workload, fig.height = 5, fig.width = 8, include = TRUE, results='hide', message=FALSE, warning=FALSE}
plot(wp@team_schedule)
```

### Saving your workplan

```{r export_workplan, include = TRUE, results='hide', message=FALSE, warning=FALSE}
export_workplan(wp, excel_file_name = "my-workplan.xlsx")
```

### Importing your workplan

```{r import_workplan, include = TRUE, results='hide', message=FALSE, warning=FALSE}
wp <- import_workplan(excel_file_name = "my-workplan.xlsx")
```



